Verifying Demonstrations

### 2017-08-18 SystemModel.tex
Adds def of participation proof

\begin{definition}[Protest]
  A \emph{subprotest} is a tuple \((id; t_s, t_e; x, y)\), where
  \(id\in \Z_{2^\lambda}\) is an identifier,
  \((t_s, t_e)\in \R^2\) is a time interval,
  \((x, y)\in \R^2\) are the coordinates of the location.
  A \emph{protest} is a set of subprotests.
\end{definition}

\begin{frame}<presentation>
\begin{definition}[Protest]
  \begin{itemize}
    \item A \emph{subprotest} is a tuple \((id; t_s, t_e; x, y)\), where
    \item \(id\in \Z_{2^\lambda}\) is an identifier,
    \item \((t_s, t_e)\in \R^2\) is a time interval,
    \item \((x, y)\in \R^2\) are the coordinates of the location.
    \item A \emph{protest} is a set of subprotests.
  \end{itemize}
\end{definition}
\end{frame}

@@

>>>>

\begin{definition}[Protest]\label{DefProtest}
  A \emph{subprotest} is a tuple \((id; t_s, t_e; x, y)\), where
  \(id\in \Z_{2^\lambda}\) is an identifier,
  \((t_s, t_e)\in \R^2\) is a time interval,
  \((x, y)\in \R^2\) are the coordinates of the location.
  A \emph{protest} is a set of subprotests sharing the same \(id\).
\end{definition}

\begin{frame}<presentation>
\begin{definition}[Protest]
  \begin{itemize}
    \item A \emph{subprotest} is a tuple \((id; t_s, t_e; x, y)\), where
    \item \(id\in \Z_{2^\lambda}\) is an identifier,
    \item \((t_s, t_e)\in \R^2\) is a time interval,
    \item \((x, y)\in \R^2\) are the coordinates of the location.
    \item A \emph{protest} is a set of subprotests sharing the same \(id\).
  \end{itemize}
\end{definition}
\end{frame}

@@

Each participant who want to be counted must submit a participation proof.
The proof must be associated with the protest, i.e.\ contain its \(id\).
Furthermore it must provide the time and the location of the participation.
More formally, we define a participation proof as follows.

\begin{definition}[Participation proof]
  A \emph{participation proof} is a tuple \((id; t_s, t_e; x, y; \sigma)\), 
  where
  \(id, t_s, t_e, x, y\) are as in \cref{DefProtest}.
  \(\sigma\) is a signature vouching for participation.
\end{definition}

\begin{frame}
  \mode<presentation>{
  \begin{definition}[Participation proof]
    \begin{itemize}
      \item A \emph{participation proof} is a tuple \((id; t_s, t_e; x, y; 
          \sigma)\), where
      \item \(id, t_s, t_e, x, y\) are as before.
      \item \(\sigma\) is a signature vouching for participation.
    \end{itemize}
  \end{definition}

  \pause
  }
\begin{question}
  How should this one relate to the \acp{LP} and blockchain?
\end{question}
\end{frame}
